---
title: "Automatic Responses to Acoustically Rough Intervals"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
output: 
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
    theme: united
    highlight: tango
---

# Release notes

_Created: 2/2/2021_.

These files contains the data and analysis scripts for "Automatic Responses to Acoustically Rough Intervals" concerning the reaction time data. See also the repository related to  [computational_models](https://tuomaseerola.github.io/primingroughness/).

All data files are available at OSF repository: [https://osf.io/zmjpd/](https://osf.io/zmjpd/).

# Main data files

* `RT_Data_Raw.csv`: PsyToolkit Data pasted into a big csv file.
* `FULL_Data_munged.csv`: RT_Data_Raw subject to `1_Munge_Script.R`.
* `Wang_results.csv`: Data for Figure 3.
* `cents_and_interval_labels.txt`: labels for Figure 1.

# R Scripts

* `1_Munge_Script`: Deletes timeouts, each participants RT data is fitted with Gamma distribution. Outliers (i.e. RTs outside 250ms<RT<95th percentile of Gamma) and incorrect answers are deleted. Note that running this script takes considerable amount of time due to bootstrapping. It can be by-passed by reading the data provided by this script ("FULL_Data_munged.csv").
* `2_GLMModel.R`: Fits GLMM model to data, tests for significance. Two versions...inverse Gaussian or Gamma as underlying distribution: no difference to pattern of significance.
* `3_Contrasts_Roughness_Harmonicity.R`: Make sure script 2 is run first; planned contrasts for High and Low Delta_Roughness and Delta_Harmonicity. 
* `4_Correlation_Wang.R`: Simple correlation test between Delta_Roughness for the expanded data to include artificial intervals. Uses raw (i.e. untransformed Wang roughness values). 
* `5_Roughness_LHE.R`: Compares Low vs (High and Extreme) with Low vs High vs Extreme. [NB: as we collapse across each participant to create a priming index, we switch to simple lm rather than glmer (i.e we don't have random effect of participant).
* `6_Figure_1.R`: creates Figure 1, needs cents_and_interval_labels.txt
* `7_Figure_2.R`: creates Figure 2
* `8_Figure_3.R`: creates Figure 3, needs Wang_results.csv
* `9_Supplementary_Wilcox_Test.R`: Tests for congruency effects for each pair of intervals seperately
* `10_KSTESTS.R`: Checks that data fits Gamma distributions

## Auxiliary data (Computational models)

Separate repository produces the predictions by computational models (roughness and harmonicity). The model predictions are also compared to each other and to empirical data (the results past rating studies involving consonance and dissonance). The way the predictions are created (separation into High and Low deltas) are also created by the these analyses. Also, the stimulus visualisations are included in the scripts.

See [computational_models](https://tuomaseerola.github.io/primingroughness/).

## Run GLMM and contrasts

```{r,echo=TRUE,results='asis',warning=FALSE,message=FALSE}
# Only run if needed.
# source('1_Munge_Script.R')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,comment=NA)
```

```{r,echo=T,results='asis',warning=FALSE,message=FALSE,include=TRUE,cache=TRUE}
source('2_GLMModel.R')
source('3_Contrasts_Roughness_Harmonicity.R')
```

## Correlations between Roughness and priming

```{r,echo=T,warning=FALSE,message=FALSE,include=TRUE}
source('4_Correlation_Wang.R')
```

## Additional contrasts (high and extreme)

```{r,echo=T,results='asis',warning=FALSE,message=FALSE,include=TRUE}
source('5_Roughness_LHE.R')
```

## Additional tests
```{r,echo=T,results='asis',warning=FALSE,message=FALSE,include=TRUE}
source('9_Supplementary_Wilcox_Test.R')
source('10_KSTESTS.R')
```

# Figures

* `6_Figure_2.R`: creates Figure 1, needs `cents_and_interval_labels.txt`.

* `7_Figure_2.R`: creates Figure 2

* `8_Figure_3.R`: creates Figure 3, needs `Wang_results.csv`

## Create Figure 1

```{r, echo=T,warning=FALSE,message=FALSE}
source('7_Figure_1.R')
```

## Create Figure 2

```{r, echo=T,warning=FALSE,message=FALSE}
source('6_Figure_2.R')
```

## Create Figure 3

```{r, echo=T,warning=FALSE,message=FALSE}
source('8_Figure_3.R')
```

# Appendix

```{r, echo=T}
sessionInfo()
```
